\documentclass[11pt, a4paper]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}

\firstname{Peter}
\familyname{Zankov}

\address{Zhukovskij}{Moscow region, Russia}
\phone{+7 915 107-62-06}
\email{pzankov@yandex.ru}

\begin{document}

\makecvtitle



\section{Summary}

\cvline{Specialization}{System programmer.}

\cvline{Skills}{C, Assembler, Linux, GNU~toolchain, Subversion, Doxygen, LaTeX.}



\section{Experience}

\cventry{2013--present}{Software engineer}{LLC "Aviaavtomatika Design Bureau"}{Kursk}{}
	{Writing OS drivers and user space software for the helicopter flight recorder.
	\begin{itemize}
	\item Wrote ARINC653 API layer for common OS drivers;
	\item Deployed WISE-Technique RTOS on cutomer's embedded hardware system.
	\end{itemize}}

\cventry{2012--present}{Software engineer}{LLC "WISE-Technique"}{Zhukovskij}{}
	{Developing microkernel real time operating system conforming ARINC 653 and POSIX.
	\begin{itemize}
	\item Wrote OS kernel;
	\item Added multi-arch and multi-core support for PowerPC and IA-32;
	\item Wrote drivers for PCI, SATA, Ethernet;
	\item Automated conformance testing with KVM;
	\item Wrote GDB server for remote debugging of user programs.
	\end{itemize}}

\cventry{2012--2012}{Software engineer}{FSUE "Flight Research Center"}{Zhukovskij}{}
	{
	\begin{itemize}
	\item Migrated OpenGL software from X11 to Wayland;
	\item Wrote video tracking software for aircraft bomb targeting.
	\end{itemize}}

\cventry{2008--2012}{Software engineer}{JSC "V.V. Tikhomirov Scientific Research Institute of Instrument Design"}{Zhukovskij}{}
   {Developing software and firmware for side-scan and phased array sonars.
   \begin{itemize}
	\item Wrote FPGA firmware for signal synthesis and digitizing;
	\item Wrote FPGA device driver for Linux;
	\item Wrote user space cross-platform software for sonar control and data processing;
	\item Added raw data geographic layout mechanism.
	\end{itemize}}



\section{Education}

\cventry{2011}{Master of Applied Mathematics and Physics}{Moscow Institute of Physics and Technology}{Russia}{}{}



\section{Languages}

\cvitemwithcomment{English}{Upper Intermediate}{}

\cvitemwithcomment{Russian}{Native}{}

\end{document}
